Clustering, profiling and plots

### 2024-09-27 data/03-clustering-and-profiling.qmd
Still working on the draft...

Normalize number of opportunities to min-max range:
```{r}
access_15_aggregated <- access_15_aggregated |>
  mutate(copp_isc_norm = ifelse(tot_copp_isc != 0, (copp_isc - min(tot_copp_isc))/(max(tot_copp_isc) - min(tot_copp_isc)), 0))
```

>>>>

Normalize number of opportunities to min-max range:
*MAYBE FIX THIS?? See 04*
```{r}
access_15_aggregated <- access_15_aggregated |>
  mutate(copp_isc_norm = ifelse(tot_copp_isc != 0, (copp_isc - min(tot_copp_isc))/(max(tot_copp_isc) - min(tot_copp_isc)), 0))
```
